Reading main files and preparing data sets

### 2025-04-04 data-raw/01-preprocessing-episode-files.Rmd
Updating the package with the new 2022 data set.

The six survey themes listed above are repeated every five years. In
addition to the central topic, each cycle includes new content that
addresses emerging and policy-relevant issues, collecting detailed
socio-demographic information, such as age, gender, education, religion,
ethnicity, income, etc. Time-use surveys collect data on all human
activities and can inform a wide range of policies. In particular, three
key themes have been identified as essential for policymaking and for
which no other data source is adequate: unpaid work and non-market
production, well-being, and gender equality. Leisure time, work-life
balance, health, commuting, culture, and sports are among the other
topics covered by time-use surveys. In addition, statistics Canada has
been conducting time-use surveys at five to seven year intervals since
1986, with the most recent being in 2015 (1986, 1992, 1998, 2005, 2010,
and 2015). The time use collects information on participation of
respondents and time spent on a wide range of day-to-day activities
using a 24-hour retrospective diary. Also, information is collected on
the location of these activities (e.g., at home, at work, etc.) and, for
non-personal activities, the people who were present with the respondent
at the time of the activity.

@@

```{r}
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(here) # A Simpler Way to Find Your Files
library(readxl) # Read Excel Files
library(tidyr) # Tidy Messy Data
library(usethis) # Automate Package and Project Setup
library(fitdistrplus) # Estimates distribution parameters
library(purrr) # Provides a complete and consistent set of tools for working with functions and vectors
```

@@

[^4]:  whether 1986, 1992, 1998, 2005, 2010 or 2015. Note: There is no
    data on cycling for the 1986 GSS survey.

@@

```{r}
# Episode File
gss_e_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-e.csv"))

# Main File
gss_m_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-m.csv"))
```

@@

```{r}
# Episode File
gss_e_2010 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2010/gss-12M0018-E-2010-c-24-tus-ef_F1.csv"))

# Main File
gss_m_2010 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2010/gss-12M0018-E-2010-c-24-tus-mf_F1.csv"))
```

@@

```{r}
# Episode File
gss_e_2005 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2005/gss-12M0019-E-2005-c-19-e_F1.csv"))

# Main File
gss_m_2005 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2005/gss-12M0019-E-2005-c-19-m_F1.csv"))
```

@@

```{r}
# Episode File
gss_e_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12e_F1.csv"))

# Main File
gss_m_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12-m_F1.csv"))
```

@@

```{r}
# Episode File
gss_e_1992 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1992/gss-12M0007-E-1992-c-7-ep_F1.csv"))

# Main File
gss_m_1992 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1992/gss-12M0007-E-1992-c-7-m_F1.csv"))
```

@@

```{r}
# Episode File
gss_e_1986 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1986/gss-12M0002-E-1986-c-2-ep_F1.csv"))

# Main File
gss_m_1986 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1986/gss-12M0002-E-1986-c-2-main_F1.csv"))
```

@@

@@

```{r creating an integrated data}
# creating an integrated data frame from 1986 to 2015
gss_episodes <- rbind(walking_2015, cycling_2015, walking_2010, cycling_2010, walking_2005, cycling_2005, cycling_1998, walking_1998, walking_1992, cycling_1992, walking_1986)
```

>>>>

The six survey themes listed above are repeated every five years. In
addition to the central topic, each cycle includes new content that
addresses emerging and policy-relevant issues, collecting detailed
socio-demographic information, such as age, gender, education, religion,
ethnicity, income, etc. Time-use surveys collect data on all human
activities and can inform a wide range of policies. In particular, three
key themes have been identified as essential for policymaking and for
which no other data source is adequate: unpaid work and non-market
production, well-being, and gender equality. Leisure time, work-life
balance, health, commuting, culture, and sports are among the other
topics covered by time-use surveys. In addition, statistics Canada has
been conducting time-use surveys at five to seven year intervals since
1986, with the most recent being in 2022 (1986, 1992, 1998, 2005, 2010, 2015, and 2022). The time use collects information on participation of
respondents and time spent on a wide range of day-to-day activities
using a 24-hour retrospective diary. Also, information is collected on
the location of these activities (e.g., at home, at work, etc.) and, for
non-personal activities, the people who were present with the respondent
at the time of the activity.

@@

```{r}
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(here) # A Simpler Way to Find Your Files
library(readxl) # Read Excel Files
library(tidyr) # Tidy Messy Data
library(usethis) # Automate Package and Project Setup
library(fitdistrplus) # Estimates distribution parameters
library(purrr) # Provides a complete and consistent set of tools for working with functions and vectors
library(foreign) # To read SSPS files
library(haven) # To read SAS files
```

@@

[^4]:  whether 1986, 1992, 1998, 2005, 2010, 2015, or 2022. Note: There is no
    data on cycling for the 1986 GSS survey.

@@

```{r}
# Episode File
gss_e_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-e.csv"))# Original file
#gss_e_2015 <- read.csv(paste0(here(), "/data-raw/2015-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
gss_m_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-m.csv")) # Original file
#gss_m_2015 <- read.csv(paste0(here(), "/data-raw/2015-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
gss_e_2010 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2010/gss-12M0018-E-2010-c-24-tus-ef_F1.csv")) # Original file
#gss_e_2010 <- read.csv(paste0(here(), "/data-raw/2010-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
gss_m_2010 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2010/gss-12M0018-E-2010-c-24-tus-mf_F1.csv")) # Original file
#gss_m_2010 <- read.csv(paste0(here(), "/data-raw/2010-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
gss_e_2005 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2005/gss-12M0019-E-2005-c-19-e_F1.csv")) # Original file
#gss_e_2005 <- read.csv(paste0(here(), "/data-raw/2005-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
gss_m_2005 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2005/gss-12M0019-E-2005-c-19-m_F1.csv")) # Original file
#gss_m_2005 <- read.csv(paste0(here(), "/data-raw/2005-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
gss_e_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12e_F1.csv")) # Original file
#gss_e_1998 <- read.csv(paste0(here(), "/data-raw/1998-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
gss_m_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12-m_F1.csv")) # Original file
#gss_m_1998 <- read.csv(paste0(here(), "/data-raw/1998-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
gss_e_1992 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1992/gss-12M0007-E-1992-c-7-ep_F1.csv")) # Original file
#gss_e_1992 <- read.csv(paste0(here(), "/data-raw/1992-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
gss_m_1992 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1992/gss-12M0007-E-1992-c-7-m_F1.csv")) # Original file
#gss_m_1992 <- read.csv(paste0(here(), "/data-raw/1992-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
gss_e_1986 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1986/gss-12M0002-E-1986-c-2-ep_F1.csv")) # Original file
#gss_e_1986 <- read.csv(paste0(here(), "/data-raw/1986-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
gss_m_1986 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1986/gss-12M0002-E-1986-c-2-main_F1.csv")) # Original file
#gss_m_1992 <- read.csv(paste0(here(), "/data-raw/1986-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

## GSS 2022

Read the Episode and Main files of the 2022 GSS survey:

```{r}
# Episode File
gss_e_2022_spss <- read.spss(paste0(here(), "/data-raw/source-files/Time-use-2022/gss_tu_episode_2022_pumf_v1.sav"), to.data.frame = TRUE)# Original file

gss_e_2022_sas <- read_sas(paste0(here(), "/data-raw/source-files/Time-use-2022/gss_tu_episode_2022_pumf_v1.sas7bdat")) # Original file

#gss_e_2022 <- read.csv(paste0(here(), "/data-raw/2022-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
gss_m_2022 <- read.spss(paste0(here(), "/data-raw/source-files/Time-use-2022/gss_tu_main_2022_pumf_v1.sav"), to.data.frame = TRUE) # Original file

#gss_m_2022 <- read.csv(paste0(here(), "/data-raw/2022-gss-m-reproducibility.csv")) # Subset for reproducibility
```

### Walking 2022

```{r}
# walking 2022
# Creating data of origins and destinations of walking trip 2022
inds_spss <- which(gss_e_2022_spss$LOCATION == 'Travel - Walk')
rows_spss <- lapply(inds_spss, function(x) (x-1):(x+1))

inds_sas <- which(gss_e_2022_sas$LOCATION == 3315)
rows_sas <- lapply(inds_sas, function(x) (x-1):(x+1))
```

[^5]: Specifically for the 2022 GSS survey, `TUI_01` refers to the
    activity code. We'll change the name of this column to be match the
    name of the activity code variable in the others surveys.

```{r}
walking_2022_spss <- gss_e_2022_spss |>
  dplyr::slice(unlist(rows_spss)) |>
  dplyr::select(PUMFID:ACTIVITY, DURATION:ENDTIME) |> 
  mutate(origin = lag(LOCATION),
         destination = lead(LOCATION)) |>
  filter(LOCATION == 'Travel - Walk') %>% 
  mutate(PUMFID = as.factor(PUMFID), 
         INSTANCE = as.factor(INSTANCE)) %>% 
  dplyr::select(-c(LOCATION)) %>% 
  dplyr::rename(act_label = ACTIVITY)

walking_2022_sas <- gss_e_2022_sas |>
  dplyr::slice(unlist(rows_sas)) |>
  dplyr::select(PUMFID, INSTANCE, LOCATION, ACTIVITY) |> 
  mutate(origin = lag(LOCATION),
         destination = lead(LOCATION)) |>
  dplyr::filter(LOCATION == 3315) %>% 
  mutate(PUMFID = as.factor(PUMFID), 
         INSTANCE = as.factor(INSTANCE)) %>% 
  dplyr::rename(ACTCODE = ACTIVITY)
```

```{r}
walking_2022_spss <- walking_2022_spss |>
  filter(origin == 'At home or on property' | 
           origin == 'At place of work or school' | 
           origin == 'Grocery store, other stores or mall'| 
           origin == 'In the neighbourhood'| 
           origin == 'Sports centre, field or arena'| 
           origin == 'Outdoors'| 
           origin == 'Restaurant, bar or club'| 
           origin == 'At someone else\'s home or property'| 
           origin == 'Medical, dental or other health clinic'| 
           origin == 'Library, museum or theatre'| 
           origin == 'Place of worship' |
           origin == 'Away at business') |>
  mutate(orig_label =
           case_when(origin == 'At home or on property' ~ "Home", 
                     origin == 'At place of work or school' ~ "Work or school",
                     origin == 'Away at business' ~ "Business",
                     origin == 'At someone else\'s home or property' ~ "Other's home",
                     TRUE ~ origin),
         orig_label = factor(orig_label))
```

```{r}
walking_2022_spss <- walking_2022_spss |>  
  filter(destination == 'At home or on property' | 
           destination == 'At place of work or school' | 
           destination == 'Grocery store, other stores or mall'| 
           destination == 'In the neighbourhood'| 
           destination == 'Sports centre, field or arena'| 
           destination == 'Outdoors'| 
           destination == 'Restaurant, bar or club'| 
           destination == 'At someone else\'s home or property'| 
           destination == 'Medical, dental or other health clinic'| 
           destination == 'Library, museum or theatre'| 
           destination == 'Place of worship' |
           destination == 'Away at business') |>
  mutate(dest_label =
           case_when(destination == 'At home or on property' ~ "Home", 
                     destination == 'At place of work or school' ~ "Work or school",
                     destination == 'Away at business' ~ "Business",
                     destination == 'At someone else\'s home or property' ~ "Other's home",
                     TRUE ~ destination), 
         dest_label = factor(dest_label))
```

```{r}
walking_2022 <- walking_2022_spss %>% 
   dplyr::select(-c(origin,destination)) %>% 
   left_join(walking_2022_sas, by = c('PUMFID', 'INSTANCE'))

walking_2022 <- walking_2022 |>
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION,
                origin, destination, orig_label, dest_label) |>
  mutate(YEAR = 2022,
         MODE = "Walking") 
```

Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
gss_m_2022 <- gss_m_2022 %>%
  dplyr::select(PUMFID,LUC_RST,PRV) %>%
  dplyr::rename(LUC = LUC_RST, 
                Province = PRV) %>% 
  mutate(PRV = 
           case_when(Province == "Newfoundland and Labroador" ~ 10,
                     Province == "Prince Edward Island" ~ 11,
                     Province == "Nova Scotia" ~ 12,
                     Province == "New Brunswick" ~ 13,
                     Province == "Quebec" ~ 24,
                     Province == "Ontario" ~ 35,
                     Province == "Manitoba" ~ 46,
                     Province == "Saskatchewan" ~ 47,
                     Province == "Alberta" ~ 48,
                     Province == "British Columbia" ~ 59),
         Pop_centre =
           case_when(LUC == 'Larger urban population centres (CMA/CA)' ~ "CMA/CA",
                     LUC == 'Prince Edward Island' ~ "non CMA/CA",
                     LUC == 'Rural areas/small population centres (non-CMA/CA)' ~ "non CMA/CA"),
         LUC_RST =
           case_when(LUC == 'Larger urban population centres (CMA/CA)' ~ 1,
                     LUC == 'Prince Edward Island' ~ 3,
                     LUC == 'Rural areas/small population centres (non-CMA/CA)' ~ 2))

walking_2022 <- walking_2022 |> 
  left_join(gss_m_2022, by = 'PUMFID') |>  # Merging the two tables
  dplyr::select(names(walking_2015))

for (col in names(walking_2015)) {
  target_class <- class(walking_2015[[col]])
  walking_2022[[col]] <- match.fun(paste0("as.", target_class[1]))(walking_2022[[col]])
}
```

```{r}
walking_2022 |> 
  group_by(orig_label, 
           dest_label) |>
  count() |>
  pivot_wider(names_from = "dest_label", values_from = "n")
```

```{r include=FALSE}
walking_2022 |>
  filter(orig_label == "Home" & dest_label == "Home")
```

See `PUMFID` == 1205 and check the walking episode:

```{r}
gss_e_2022_spss |>
  filter(PUMFID == '1205') |>
  slice(unique(c(which(LOCATION == 'Travel - Walk') - 1, 
                 which(LOCATION == 'Travel - Walk'),
                 which(LOCATION == 'Travel - Walk') + 1))) |>
  dplyr::select(PUMFID, INSTANCE, ACTIVITY, LOCATION, DURATION)
```

The person was at home doing regular household tasks, then went for
walk that lasted 20 minutes, came back home and returned to the household tasks for more 180 minutes.

```{r}
usethis::use_data(walking_2022, 
                  overwrite = TRUE)
```

### Cycling 2022

```{r}
# cycling 2022
# Creating data of origins and destinations of cycling trip 2022
inds_spss <- which(gss_e_2022_spss$LOCATION == 'Travel - Bicycle')
rows_spss <- lapply(inds_spss, function(x) (x-1):(x+1))

inds_sas <- which(gss_e_2022_sas$LOCATION == 3318)
rows_sas <- lapply(inds_sas, function(x) (x-1):(x+1))
```

Now, we'll select all the rows with cycling episodes in the GSS survey,
selecting the columns that we are interested[^5], and already creating
the origin and destination variables:

[^5]: Specifically for the 2022 GSS survey, `TUI_01` refers to the
    activity code. We'll change the name of this column to be match the
    name of the activity code variable in the others surveys.

```{r}
cycling_2022_spss <- gss_e_2022_spss |>
  dplyr::slice(unlist(rows_spss)) |>
  dplyr::select(PUMFID:ACTIVITY, DURATION:ENDTIME) |> 
  mutate(origin = lag(LOCATION),
         destination = lead(LOCATION)) |>
  filter(LOCATION == 'Travel - Bicycle') %>% 
  mutate(PUMFID = as.factor(PUMFID), 
         INSTANCE = as.factor(INSTANCE)) %>% 
  dplyr::select(-c(LOCATION)) %>% 
  dplyr::rename(act_label = ACTIVITY)

cycling_2022_sas <- gss_e_2022_sas |>
  dplyr::slice(unlist(rows_sas)) |>
  dplyr::select(PUMFID, INSTANCE, LOCATION, ACTIVITY) |> 
  mutate(origin = lag(LOCATION),
         destination = lead(LOCATION)) |>
  dplyr::filter(LOCATION == 3318) %>% 
  mutate(PUMFID = as.factor(PUMFID), 
         INSTANCE = as.factor(INSTANCE)) %>% 
  dplyr::rename(ACTCODE = ACTIVITY)
```

```{r}
cycling_2022_spss <- cycling_2022_spss |>
  filter(origin == 'At home or on property' | 
           origin == 'At place of work or school' | 
           origin == 'Grocery store, other stores or mall'| 
           origin == 'In the neighbourhood'| 
           origin == 'Sports centre, field or arena'| 
           origin == 'Outdoors'| 
           origin == 'Restaurant, bar or club'| 
           origin == 'At someone else\'s home or property'| 
           origin == 'Medical, dental or other health clinic'| 
           origin == 'Library, museum or theatre'| 
           origin == 'Place of worship' |
           origin == 'Away at business') |>
  mutate(orig_label =
           case_when(origin == 'At home or on property' ~ "Home", 
                     origin == 'At place of work or school' ~ "Work or school",
                     origin == 'Away at business' ~ "Business",
                     origin == 'At someone else\'s home or property' ~ "Other's home",
                     TRUE ~ origin),
         orig_label = factor(orig_label))
```

```{r}
cycling_2022_spss <- cycling_2022_spss |>  
  filter(destination == 'At home or on property' | 
           destination == 'At place of work or school' | 
           destination == 'Grocery store, other stores or mall'| 
           destination == 'In the neighbourhood'| 
           destination == 'Sports centre, field or arena'| 
           destination == 'Outdoors'| 
           destination == 'Restaurant, bar or club'| 
           destination == 'At someone else\'s home or property'| 
           destination == 'Medical, dental or other health clinic'| 
           destination == 'Library, museum or theatre'| 
           destination == 'Place of worship' |
           destination == 'Away at business') |>
  mutate(dest_label =
           case_when(destination == 'At home or on property' ~ "Home", 
                     destination == 'At place of work or school' ~ "Work or school",
                     destination == 'Away at business' ~ "Business",
                     destination == 'At someone else\'s home or property' ~ "Other's home",
                     TRUE ~ destination), 
         dest_label = factor(dest_label))
```

```{r}
cycling_2022 <- cycling_2022_spss %>% 
   dplyr::select(-c(origin,destination)) %>% 
   left_join(cycling_2022_sas, by = c('PUMFID', 'INSTANCE'))

cycling_2022 <- cycling_2022 |>
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION,
                origin, destination, orig_label, dest_label) |>
  mutate(YEAR = 2022,
         MODE = "Cycling") 
```

Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
cycling_2022 <- cycling_2022 |> 
  left_join(gss_m_2022, by = 'PUMFID') |>  # Merging the two tables
  dplyr::select(names(walking_2015))

for (col in names(walking_2015)) {
  target_class <- class(walking_2015[[col]])
  cycling_2022[[col]] <- match.fun(paste0("as.", target_class[1]))(cycling_2022[[col]])
}
```

```{r}
cycling_2022 |> 
  group_by(orig_label, 
           dest_label) |>
  count() |>
  pivot_wider(names_from = "dest_label", values_from = "n")
```

The table above shows that the most common destination for a cycling trip
that starts at home are `Home` and `Work or school`. It also shows that the second most common cycling trip is from `Grocery store, other stores or mall` to `Home`. Notice, though,
that quite a few trips start *and* end at Home. What are those supposed
to be?

```{r include=FALSE}
cycling_2022 |>
  filter(orig_label == "Home" & dest_label == "Home")
```

See `PUMFID` == 5002 and check the cycling episode:

```{r}
gss_e_2022_spss |>
  filter(PUMFID == '5002') |>
  slice(unique(c(which(LOCATION == 'Travel - Bicycle') - 1, 
                 which(LOCATION == 'Travel - Bicycle'),
                 which(LOCATION == 'Travel - Bicycle') + 1))) |>
  dplyr::select(PUMFID, INSTANCE, ACTIVITY, LOCATION, DURATION)
```

The person was at home doing `Culture, sports events, hobbies, leisure or outdoor activity`, then went for cycling trip that lasted 60 minutes, came back home and spent 120 minutes
`reading, whatching TV or listening music`. So, this was a recreational/leisure
trip!

```{r}
usethis::use_data(cycling_2022, 
                  overwrite = TRUE)
```

@@

```{r creating an integrated data}
# creating an integrated data frame from 1986 to 2015
gss_episodes <- rbind(walking_2022, cycling_2022, walking_2015, cycling_2015, walking_2010, cycling_2010, walking_2005, cycling_2005, cycling_1998, walking_1998, walking_1992, cycling_1992, walking_1986)
```

### 2025-04-04 data-raw/02-calculating-impedances.Rmd
Updating the package with the new 2022 data set.

In this R markdown, we'll calculate the impedance functions for walking and cycling for each GSS year (from 1986 to 2015).

@@

Similar as we did before, the next chunk selects the best impedance function, using the `test_distributions_weighted` and `lowest_aic` functions for each destination, transportation mode and year. The name pattern is as follows: `f_year_mode_dest` + `dest_label`, which means that `f_1986_Walking_destHome` displays the best function for the year 1986, walking mode, Home destination.
/000
```{r}
for(year in unique(gss_episodes$YEAR)){

@@

          assign(paste0("f_",year, "_", mode, "_dest", destino),
               test_distributions_weighted(
               x = gss_subset$DURATION,
               weights = round(gss_subset$WGHT_EPI)))
        }
    }
  }
}
```
After selecting the best function for every combination of destination, transportation mode and year, the next two chunks will apply the functions in all surveys, adding the information with the best function and its parameters, AIC/BIC/loglik values, and count of episodes that were used to calculate the function:

>>>>

In this R markdown, we'll calculate the impedance functions for walking and cycling for each GSS year (from 1986 to 2022).

@@

Similar as we did before, the next chunk selects the best impedance function, using the `test_distributions_weighted` and `lowest_aic` functions for each destination, transportation mode and year. The name pattern is as follows: `f_year_mode_dest` + `dest_label`, which means that `f_1986_Walking_destHome` displays the best function for the year 1986, walking mode, Home destination.

```{r}
for(year in unique(gss_episodes$YEAR)){

@@

          assign(paste0("f_",year, "_", mode, "_dest", destino),
               test_distributions_weighted(
               x = gss_subset$DURATION,
               weights = round(gss_subset$WGHT_EPI)))
        }
    }
  }
}
```

After selecting the best function for every combination of destination, transportation mode and year, the next two chunks will apply the functions in all surveys, adding the information with the best function and its parameters, AIC/BIC/loglik values, and count of episodes that were used to calculate the function:

### 2025-04-04 data-raw/03-preprocessing-main-files.Rmd
Updating the package with the new 2022 data set.

```{r read-libraries}
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(here) # A Simpler Way to Find Your Files
library(readxl) # Read Excel Files
library(tidyr) # Tidy Messy Data
library(usethis) # Automate Package and Project Setup
library(purrr) # Provides a complete and consistent set of tools for working with functions and vectors
```

@@

>>>>

```{r read-libraries}
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(here) # A Simpler Way to Find Your Files
library(readxl) # Read Excel Files
library(tidyr) # Tidy Messy Data
library(usethis) # Automate Package and Project Setup
library(purrr) # Provides a complete and consistent set of tools for working with functions and vectors
library(foreign) # Read SPSS files
```

@@

## GSS 2022

```{r reading-2022-main-file}
# Main File
gss_m_2022 <- read.spss(paste0(here(), "/data-raw/source-files/Time-use-2022/gss_tu_main_2022_pumf_v1.sav"), to.data.frame = TRUE) # Original file
```

The main data set for 2022 is already labeled and only needs a selection of socioeconomic and demographic variables:

```{r filtering-variables-2022}
gss_main_2022 <- gss_m_2022 %>%
  dplyr::select("PUMFID", "WGHT_PER","SURVMNTH", "PRV", "LUC_RST", "REGION",  "HSDSIZEC","AGEGR10", "GENDER2",
"MARSTAT", "PHSDFLG", "AGEPRC",  "GENPR2",  "COUPGEN2","CHH0017C","CHH0004C","CHH0514C","CHH1517C","CXRFLAG",
"PARNUM",  "SENFLAG", "MULTIGEN","DDEV_FL", "DDEX_FL", "DFLEX_FL","DHEAR_FL","DLRN_FL", "DMEM_FL", "DMENT_FL",
 "DMOB_FL", "DPAIN_FL","DUNK_FL", "DVIS_FL", "DDIS_FL", "DTYPER",  "DCLASS",  "TCS_110", "TCS_120", "TCS_130",
 "TCS_140", "TCS_150", "TCS_160", "TCS_170", "TCS_180", "TCS_190", "TCS_200",  "GEN_01",  "GEN_02",  "SRS_10",  "MSS_130", "ACT7DAYC","MRW_05C", "MRW_D40A",
"MRW_D40B","WET_120",  "WHW_230", "WHWD140G","TLWK_01A","TLWK_06","WLYD170G",
"ATT_120", "ATT_130", "ATT_131",
"ATT_150C","ATT_160", "ATT_170",
"CTW_140A","CTW_140B","CTW_140C","CTW_140D",
"CTW_140E","CTW140GR","CTW_140I","CTW_150G","CTW_160", "CTW_170", "CTW_180", "CTW_190", "CTW_210", "CTW_215",
"ED_05",  "MAP_110C","MAP_D40A","DOR_110C","IM_01A",  "YRARRI_C","BPP_01A", "BPR_20", "ABM_01A",
"AIP_01A", "VISMINFL","VISPRFL", "REL_02",  "RELIGFLG","INC_C",  
"FAMINC_C","GTU_110", "GTU_130",  "DDAY",  "DVTDAY")
```

Save data in R format for later use:
```{r save-data-2022}
usethis::use_data(gss_main_2022, 
                  overwrite = TRUE)
```
